---
title: "Your Manuscript Title Here: A Comprehensive Analysis"
subtitle: ""  # Optional - remove if not needed
shorttitle: "Short Title for Headers"  # Used in running headers

# ============================================================================
# AUTHOR INFORMATION
# ============================================================================
# Include complete information for all authors
# Mark the corresponding author with "corresponding: true"
# Include ORCID IDs for all authors (obtain from https://orcid.org/)
author:
  - name: First Author Name
    corresponding: true
    orcid: 0000-0000-0000-0000
    email: first.author@institution.edu
    affiliations:
      - id: aff1
        name: Institution Name
        department: Department or School Name
        address: Street Address
        city: City
        region: State/Province
        postal-code: 12345
        country: Country

  - name: Second Author Name
    orcid: 0000-0000-0000-0001
    email: second.author@institution.edu
    affiliations:
      - ref: aff1  # References the affiliation defined above
      - id: aff2   # Second affiliation for this author
        name: Second Institution Name
        city: City
        country: Country

# ============================================================================
# ABSTRACT
# ============================================================================
# For BMC and most health journals, use a structured abstract with:
# Background, Methods, Results, Conclusions
abstract: |
  **Background:** Provide the context and rationale for the study. State the
  specific objectives or research questions being addressed. Keep this section
  concise (2-4 sentences).

  **Methods:** Briefly describe the study design, data sources, study population,
  main variables, and analytical methods used. Be specific enough that readers
  understand what was done (4-6 sentences).

  **Results:** Present the main findings with key numerical results. Include
  specific statistics where relevant. Focus on results that address the main
  objectives (4-6 sentences).

  **Conclusions:** State the main conclusions drawn from the results and their
  implications for policy, practice, or research. Avoid over-interpreting the
  findings (2-3 sentences).

# ============================================================================
# KEYWORDS
# ============================================================================
# Provide 3-10 keywords for indexing
# Use terms from MeSH (Medical Subject Headings) when applicable
keywords:
  - health insurance
  - universal health coverage
  - health equity
  - Kenya
  - demographic survey

# ============================================================================
# DECLARATIONS
# ============================================================================
# These sections are required by most journals

funding: |
  This study was funded by [Funding Agency Name] (Grant number: XXX-XXXX).
  The funders had no role in study design, data collection and analysis,
  decision to publish, or preparation of the manuscript. [Adapt as needed]

author-note:
  contributions: |
    **Author 1** conceptualized the study, performed the analysis, and drafted
    the manuscript. **Author 2** supervised the study, contributed to
    interpretation, and reviewed and edited the manuscript. All authors read
    and approved the final manuscript.

  disclosures:
    conflict-of-interest: |
      The authors declare that they have no competing interests.

    ethics: |
      This study used publicly available de-identified data from the [Data Source].
      The original survey received ethical approval from [Ethics Committee].
      No additional ethical approval was required for this secondary analysis.

    data-availability: |
      The data that support the findings of this study are openly available
      from [Data Source] at [URL]. Analysis code is available at [Repository URL].

# ============================================================================
# OUTPUT FORMATS
# ============================================================================
# Uncomment the format you need. You can have multiple formats active.

format:
  # Standard formats (always useful during writing and editing)
  docx:
    toc: false
    number-sections: true
    reference-doc: custom-reference.docx  # Optional: use custom Word template

  html:
    toc: true
    toc-depth: 3
    number-sections: true
    theme: cosmo
    code-fold: true
    embed-resources: true

  # PDF format (basic)
  # pdf:
  #   toc: false
  #   number-sections: true
  #   keep-tex: true

  # SPRINGER NATURE / BMC JOURNALS
  # Install with: quarto add christopherkenny/nature
  # nature-pdf:
  #   journal:
  #     cite-style: default  # Options: default, sn-nature, sn-basic, sn-mathphys-num, etc.
  #   keep-tex: true
  #   classoption:
  #     - referee  # Double-spaced for review
  #     # - lineno  # Line numbers for review

  # ELSEVIER JOURNALS (e.g., The Lancet, Cell)
  # Install with: quarto add quarto-journals/elsevier
  # elsevier-pdf:
  #   journal:
  #     name: "Journal Name"
  #     formatting: preprint  # Options: preprint, review, doubleblind
  #     model: 3p  # Options: 1p (always 1 column), 3p (flexible), 5p (always 2 column)
  #     layout: onecolumn  # Options: onecolumn, twocolumn
  #     cite-style: number  # Options: number, numbername, authoryear, super
  #   keep-tex: true

  # PLOS JOURNALS (e.g., PLOS ONE, PLOS Medicine)
  # Install with: quarto add quarto-journals/plos
  # plos-pdf:
  #   keep-tex: true

# ============================================================================
# BIBLIOGRAPHY AND CITATIONS
# ============================================================================
# Specify your bibliography file and citation style
bibliography: references.bib

# Citation Style Language (CSL) file
# Common options:
# - vancouver.csl (common in medical journals, including BMC)
# - apa.csl (American Psychological Association)
# - harvard.csl (Harvard referencing)
# Download more from: https://github.com/citation-style-language/styles
csl: vancouver.csl  # Change as needed for target journal

# ============================================================================
# DOCUMENT PROCESSING OPTIONS
# ============================================================================
editor: source

execute:
  echo: false      # Don't show code in output
  warning: false   # Don't show warnings
  message: false   # Don't show messages
  cache: false     # Set to true for long-running analyses
  freeze: auto     # Freeze computational output

# ============================================================================
# CUSTOM SETTINGS (optional)
# ============================================================================
# fig-width: 7
# fig-height: 5
# fig-dpi: 300
---

```{r}
#| label: setup
#| include: false

# Load required packages
library(tidyverse)
library(flextable)  # For formatted tables
library(gtsummary)  # For summary tables
library(scales)     # For number formatting

# Set options
options(scipen = 999)  # Avoid scientific notation

# Load analysis results
# Adjust the path to match your project structure
analysis_object <- readRDS(file.path("..", "07_derived_data", "analysis_outputs.rds"))

# Extract objects from analysis
# Adapt these based on your actual analysis output
# table1 <- analysis_object$table1
# table2 <- analysis_object$table2
# overall_stats <- analysis_object$overall_stats

# Helper functions for inline reporting
fmt_pct <- function(x, ci_low, ci_high) {
  sprintf("%.1f%% (95%% CI %.1f%% to %.1f%%)",
          100 * x, 100 * ci_low, 100 * ci_high)
}

fmt_p_value <- function(p) {
  if (is.na(p) || p == "") return("")
  if (p < 0.001) return("< 0.001")
  sprintf("%.3f", p)
}

fmt_number <- function(x) {
  comma(x)
}
```

# Background

<!--
INSTRUCTIONS:
- Provide context for the study
- Explain the rationale and importance
- State specific objectives or research questions
- Keep focused and concise (typically 3-5 paragraphs)
-->

[First paragraph: General context and importance of the topic]

[Second paragraph: What is known and gaps in knowledge]

[Third paragraph: What this study adds]

[Final paragraph: Specific objectives]

# Methods

## Study design and data source

<!--
Describe:
- Study design (cross-sectional, cohort, etc.)
- Data source and survey details
- Time period covered
- Ethical approval
-->

[Describe the study design and data source]

## Study population

<!--
Describe:
- Inclusion and exclusion criteria
- Sample size
- Sampling methods
- Weighting procedures (if applicable)
-->

[Describe the study population]

## Variables and measurements

### Outcome variables

[Describe primary and secondary outcomes]

### Exposure variables

[Describe main exposures of interest]

### Covariates

[Describe other variables included in the analysis]

## Statistical analysis

<!--
Describe:
- Descriptive statistics methods
- Inferential statistics (tests, models)
- Software used
- How missing data was handled
- Significance level (typically p < 0.05)
-->

[Describe statistical methods]

All analyses were performed using R version X.X.X (R Foundation for Statistical Computing, Vienna, Austria) [@r2024]. Survey weighting and complex survey design were accounted for using the survey package [@lumley2024]. Statistical significance was set at p < 0.05.

## Ethical considerations

[State ethical approval details and how ethical principles were addressed]

# Results

<!--
INSTRUCTIONS:
- Present results in logical order
- Use subsections for clarity
- Reference tables and figures
- Report key statistics with confidence intervals
- Don't interpret results here (save for Discussion)
-->

## Study population characteristics

<!-- Example of referencing a table -->
The study included [N] participants. @tbl-demographics shows the demographic characteristics of the study population.

```{r}
#| label: tbl-demographics
#| tbl-cap: "Demographic characteristics of study participants"

# Display your table here
# Example:
# table1_display
```

<!-- Example of inline statistics -->
The mean age was [XX] years (SD [XX]), and [XX]% were female.

## Main findings

<!-- Example of referencing a figure -->
@fig-main-results presents the main findings of the study.

```{r}
#| label: fig-main-results
#| fig-cap: "Description of what the figure shows"
#| fig-width: 7
#| fig-height: 5

# Create your figure here
# Example:
# ggplot(data, aes(x = variable1, y = variable2)) +
#   geom_point() +
#   theme_minimal() +
#   labs(x = "X-axis label", y = "Y-axis label")
```

[Describe the main findings with specific results]

## Subgroup analyses

<!-- Additional tables and analyses -->
@tbl-subgroup shows results stratified by [variable].

```{r}
#| label: tbl-subgroup
#| tbl-cap: "Subgroup analysis by [variable]"

# Display your subgroup table here
```

# Discussion

## Main findings

<!--
INSTRUCTIONS:
- Summarize key findings
- Compare with previous studies
- Discuss strengths and limitations
- Address implications
- Suggest future research
- Don't overstate conclusions
-->

[Summarize the principal findings in context]

## Comparison with other studies

[Compare your findings with previous research, noting agreements and discrepancies]

## Strengths and limitations

This study has several strengths. [List strengths]

However, limitations should be noted. [List limitations]

## Implications

[Discuss implications for policy, practice, or research]

# Conclusions

[Provide concise concluding statements based on the findings. Typically 1-2 paragraphs.]

# Abbreviations {.unnumbered}

<!--
List abbreviations alphabetically
Example:
- CI: Confidence Interval
- DHS: Demographic and Health Survey
- OR: Odds Ratio
- SD: Standard Deviation
-->

# Declarations {.unnumbered}

## Ethics approval and consent to participate {.unnumbered}

[Ethics statement - adapt based on your study]

## Consent for publication {.unnumbered}

Not applicable (for studies using publicly available de-identified data).

## Availability of data and materials {.unnumbered}

[Data availability statement]

## Competing interests {.unnumbered}

[Competing interests statement]

## Funding {.unnumbered}

[Funding statement]

## Authors' contributions {.unnumbered}

[Author contributions statement]

## Acknowledgements {.unnumbered}

[Acknowledgements if any]

# References {.unnumbered}

<!-- References will be automatically generated here -->

::: {#refs}
:::

# Supplementary Materials {.unnumbered}

<!-- Include if you have supplementary tables, figures, or appendices -->

## Supplementary Table 1 {.unnumbered}

[Additional detailed tables]

## Supplementary Figure 1 {.unnumbered}

[Additional figures]
